### 2020-04-20 final_report/methodology.tex
nicer neural network figure
fill in hyperparam counts

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Surrogate & Acronym & Implementation & Hyperparameters \\
		\midrule
		Support vector machines	& SVM & SciKit Learn & TODO \\
		Gradient boosted trees	& GBT & SciKit Learn & TODO \\
		Extremely randomized trees	& ERT & SciKit Learn & TODO \\
		AdaBoosted decision trees	& AB & SciKit Learn & TODO \\
		Gaussian process regression	& GPR & SciKit Learn & TODO \\
		$k$ nearest neighbours	& KNN & SciKit Learn & TODO \\
		Neural networks	& NN & Keras (TensorFlow) & TODO \\
		Inverse distance weighing & IDW & SMT & TODO \\
		Radial basis functions & RBF & SMT & TODO \\
		Stochastic gradient descent & SGD & SciKit Learn & TODO \\
		Ridge regression & RR & SciKit Learn & TODO \\
		Kriging & KRG & SMT & TODO \\
		\bottomrule
		\end{tabular}
	}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.20\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{1h3f}}
		\caption{$\text{1h3f}(W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.15\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{kf}}
		\caption{$\text{df}(D,W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.15\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{3pyramid}}
		\caption{$\text{3pyr}(W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.20\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{5diam}}
		\caption{$\text{5diam}(W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.20\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{kf}} % TODO
		\caption{$\text{6sym}(W)$}
	\end{subfigure}

	\caption{Various considered parametric neural architectures. All layers use ReLU
		activation and random initialisation. Information flow is indicated by
		arrows. Conections between neurons are omitted for clarity.}
	\label{fig:nn-archs}
\end{figure}

>>>>

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Surrogate & Acronym & Implementation & Hyperparameters \\
		\midrule
		Support vector machines	& SVM & SciKit Learn & 3 \\
		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
		Extremely randomized trees	& ERT & SciKit Learn & 7 \\
		AdaBoosted decision trees	& AB & SciKit Learn & 3 \\
		Gaussian process regression	& GPR & SciKit Learn & 2 \\
		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
		Neural networks	& NN & Keras (TensorFlow) & 2 \\
		Inverse distance weighing & IDW & SMT & 1 \\
		Radial basis functions & RBF & SMT & 3 \\
		Stochastic gradient descent & SGD & SciKit Learn & 13 \\
		Ridge regression & RR & SciKit Learn & 4 \\
		Kriging & KRG & SMT & 4 \\
		\bottomrule
		\end{tabular}
	}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		{\scriptsize \incfigscale{0.6}{1h3f}}
		\caption{$\text{1h3f}(W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		{\scriptsize \incfigscale{0.6}{kf}}
		\caption{$\text{df}(D,W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		{\scriptsize \incfigscale{0.6}{3pyramid}}
		\caption{$\text{3pyr}(W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		{\scriptsize \incfigscale{0.6}{5diam}}
		\caption{$\text{5diam}(W)$}
	\end{subfigure}

	\caption{Selected parametric neural network architectures. All layers except
		the last use ReLU activation. Prediction information flow is indicated by
		arrows. Conections between neurons are omitted for clarity.}
	\label{fig:nn-archs}
\end{figure}
